\chapter{Introduction}
\label{chap:introduction}

\section{Background}
\label{section:background}

Communication is an essential part of daily life, yet people with hearing disabilities often face significant 
challenges when interacting with others. Many members of the deaf community rely on sign language as 
their primary form of communication, but most hearing people do not understand it.
This gap creates communication barriers in situations such as education, healthcare, employment, and emergency services.
In Thailand, where Thai Sign Language is widely used, these challenges are even more evident due to the limited availability of 
professional interpreters, especially in urgent or everyday scenarios.

Although modern technologies such as artificial intelligence, speech recognition, and computer vision have been developed to support communication, 
existing solutions still have limitations. Many systems focus mainly on direct or word by word translation, 
which may not accurately capture the meaning, context, or natural flow of communication. Additionally, some solutions are not designed for real-time interaction 
or are not user friendly for everyday use.

Therefore, there is a need for a more effective communication system that can provide natural and continuous interpretation rather than 
simple word by word translation. Such a system should support smooth interaction between hearing disabilities individuals and hearing users 
while maintaining context and meaning during communication.

This project proposes TermTem, an AI-based communication assistant that integrates sign language recognition, speech recognition, 
conversational AI, and real time animation displayed through avatar to support real time communication between hearing disability individuals and hearing users.

\section{Problem Statement}
\label{section:problem-statement}

People with hearing disabilities often experience communication difficulties when interacting with individuals 
who do not understand Thai Sign Language. In many real life situations such as hospitals, workplaces, public services, 
or emergency cases, communication becomes difficult because sign language interpreters are not always available.
Existing solutions mainly rely on human interpreters or limited translation tools, which may be costly, unavailable, 
or not suitable for real time communication. 

In addition, many current technological solutions focus on word by word translation, which may not accurately capture the meaning,
context or natural flow of interaction between users.

Therefore, there is a need for an intelligent system that can assist in communication. Such a system should be able to translate
sign language, speech, and text in real time to reduce communication barriers and improve accessibility for people with hearing disabilities.
\newpage
\section{Solution Overview}
\label{section:solution-overview}

This project proposes TermTem, an AI-based communication assistant that integrates sign language recognition, speech recognition, 
conversational AI, and real time animation displayed through avatar to support real time communication between hearing disability individuals and hearing users.

\subsection{Features}
\label{subsection:features}

\begin{enumerate}[leftmargin=80pt]
    \item Speech to Sign Translation with Avatar: The system converts speech or text input from hearing users into Thai Sign Language animations displayed through an avatar, enabling hearing disabilities users to understand messages in a natural and visual form.
    \item Speech Recognition: The system captures and converts spoken language from hearing users into text for further processing by the system.
    \item Sign Language Animation Generation: The system generates accurate and continuous sign language animations using an avatar to represent gestures clearly and naturally, focusing on smooth communication rather than word by word translation.
    \item Conversational AI Assistant: The system uses a conversational AI model to understand user intent and generate meaningful responses, improving the quality and flow of communication.
\end{enumerate}
\subsection{Extra Features}
\label{subsection:features}

\begin{enumerate}[leftmargin=80pt]
    \item Learning Module: The system provides learning support through interactive quizzes to help users learn and improve their Thai Sign Language skills.
\end{enumerate}
\newpage
\section{Target User}
\label{section:target-user}

\begin{itemize}

\item \textbf{People with hearing disabilities}
\begin{itemize}
    \item Demographics: Individuals of all ages in Thailand who primarily use Thai Sign Language as their main form of communication.
    \item Skill level: Basic smartphone proficiency.
    \item Industry or Domain: Daily communication scenarios such as healthcare services, public services, workplaces, and emergency situations.
\end{itemize}

\item \textbf{Learners of Thai Sign Language}
\begin{itemize}
    \item Demographics: Students, educators, family members, or individuals interested in learning Thai Sign Language.
    \item Skill level: Beginners in sign language who require clear visual demonstrations and accurate sign language animations for learning.
    \item Industry or Domain: Education.
\end{itemize}

\end{itemize}

\newpage
\section{Terminology}
\label{section:terminology}
\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.5} % Adds padding for readability
\begin{tabular}{|l|p{10cm}|}
\hline
\textbf{Term} & \textbf{Description} \\ \hline
Thai Sign Language  & The primary sign language used by the deaf community in Thailand. \\ \hline
Sign Language Recognition & A computer vision technique used to detect and interpret sign language gestures. \\ \hline
Speech Recognition & Technology that converts spoken language into text. \\ \hline
Text-to-Speech  & Technology that converts text into spoken audio. \\ \hline
Conversational AI & AI technology that enables systems to understand and respond to human language. \\ \hline
Avatar Animation & A digital character used to visually represent sign language gestures. \\ \hline
\end{tabular}
\end{table}